Drawing Math

### 2022-05-12 paper/Paper.tex
main proofs
intro and abstract

\pagebreak
\section{Introduction}
- Numberphile video
- I was bored and this looked fun
- I wasn't paying attention in one of my lectures...
- This paper is purely for funs... for now

@@

\begin{remark}[Randomness assumption]
  The randomness assumption, that $(\digSumPeriodicNoJ^1, ..., \digSumPeriodicNoJ^k)$
  is drawn from a random distribution is very much not true. But, given a rational parameter
  there does seem to be some element of randomness for $\digSumPeriodic$. See \cite{OnDecSeq} for more information.
\end{remark}
\section{Conclusion}

\section{Open Questions}

>>>>

\pagebreak
\section*{Abstract}
Given an object in cartesian space, we ask whether a repeating sequence 
of spherical updates to the object's position cause it to travel on a closed path.
A spherical update to a position in $D$-dimensional space can be written as
$\left(r, \theta_1, \theta_2, ..., \theta_{D-1}\right)$.
In this paper, we consider $D-1$ non-terminating
rational numbers where for time-step $i$, the spherical updates' difference function
is given by $r' \leftarrow r$, 
$\theta_1' \leftarrow \theta_1 + \mathrm{digit}(q_1, i)$, ..., 
$\theta_{D-1}' \leftarrow \theta_{D-1} + \mathrm{digit}(q_{D-1}, i)$.
We then proceed to derive a formula for finding if the object takes a closed, repeating path.
Moreover, we explore interesting properties of this problem and
relate it to discrete log, roots of a multinomial, and center of mass.

\section{Introduction}
A glum Pittsburgh day inspired the authors to take a random walk down YouTube's recommended
when they encountered the Numberphile video on ``Plotting Pi" \cite{NumberphileVid}.
In the video, Henderson and Brady introduce the idea of taking a Python Turtle and
deriving a series of updates to its position based off of various decimal sequences, 
some rational, some irrational. More specifically, they place an object in 2D, cartesian
space starting at $(0, 0)$ and ``facing" to the right. They then take a generating number, like $\pi$ or $35/99$, 
which gives a decimal sequence ($3.14...$ and $0.\bar{35}$ respectively). 
Then, at time step $i$, $i \geq 1$, they rotate the object by the $i$th digit divided by the base of
the decimal sequence. Then, the Turtle moves a constant distance in the direction which it faces.
For example, if the second digit is 4, the turtle is rotated by $\frac{4}{10}$ths of a circle
counterclockwise at time step 2 and then moves 10 units in its new direction.
% TODO: diagram, timestep 1 --> 2 --> 3

Whenever the Turtle moves, the program draws a red line along the Turtle's path. Thus,
different lines are drawn.
The authors noticed that using rational numbers to generate the sequence often drew geometrically
aesthetic, closed shapes.

\begin{figure}[ht]
  \centering
  \includegraphics[width=8cm]{fig/Turtle1D13Div113.png}
  \caption{The closed shape generated from $\frac{13}{113} = 0.0977443609...$ in base $10$.}
\end{figure}
\begin{figure}[ht]
  \centering
  \includegraphics[width=8cm]{fig/Turtle1DNotClosed.png}
  \caption{A non-closing shape generated from $\frac{2134}{9999} = 0.\overline{2134}$ in base $10$.}
\end{figure}

Naturally, the authors were curious whether a Turtle in ``3D" would also draw 
aesthetic shapes. In other words, what if the Turtle's orientation was described
by 2 angles, pitch and yaw. The pitch and yaw would then by independently updated
by 2 decimal sequences generated from 2 rational numbers.
% TODO: figure
After writing the program, we noticed that the Turtle would often fail
to close. In other words, the Turtle would go off in one direction forever.
% TODO: picture of failing to close.
But, the Turtle \textit{sometimes} closed.

The authors then proceeded to ask why the Turtle would sometimes close and sometimes
go off into the ether. After finding a closed form solution in 3 dimensional space,
we proceeded to ask the same question in $D$ dimensional space: given $D - 1$ 
rational decimal sequences which determine the Turtle's orientation in space,
does the Turtle move in a closed shape (i.e.\ is the Turtle position always contained
within some $D$ dimensional sphere off constant radius)?

@@

Somewhat surprisingly, we can then see that probability of closure may increase exponentially
with a decreasing $k$. Moreover, a larger $\commonBase$ also increases the lower bound!

\begin{remark}[Randomness assumption]
  The randomness assumption, that $(\digSumPeriodicNoJ^1, ..., \digSumPeriodicNoJ^k)$
  is drawn from a random distribution is very much not true. But, given a rational parameter
  there does seem to be some element of randomness for $\digSumPeriodic$. See \cite{OnDecSeq} for more information.
\end{remark}
\section{Open Questions}

\section{Conclusion}
